Msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-08-03 paper.tex

\begin{figure}
\begin{center}
    \includegraphics{figures/ancestry-perf}
\end{center}
\caption{\label{fig-ancestry-perf}
    Approximate run time for \msprime\ simulations,
    for (A) small and (B) larger simulations.
    Each point is the runtime of one simulation,
    for various values of effective population size ($N$),
    genome length ($L$), and number of samples.
    Runtime scales quadratically with the product of $N$ and $L$;
    since recombination rate in these simulations was $10^{-8}$,
    the scaled recombination rate here is $\rho = NL/10^8$,
    shown on the horizontal axis.
    The black lines are quadratic fits separately in each panel
    and sample size.
}
\end{figure}

@@

More visibly to the end user, we also have a high standard for documentation,
with precise, comprehensive, and cross-linked documentation
that is automatically built from the code base
and served through the website \texttt{https://tskit.dev}.
With the goal of lowering the entry barrier to new users,
we have invested significant effort in writing examples and introductions,
and making common tasks discoverable.
We also view contributions to documentation as equally important to the project
as writing code or designing methods---what use would it be
to write reliable, stable software if no-one used it?

>>>>

\begin{figure}
\begin{center}
    \includegraphics{figures/ancestry-perf}
    \includegraphics{figures/ancestry-perf-expected}
\end{center}
\caption{\label{fig-ancestry-perf}
    \jkcomment{This is a temporary version of the figure pending the outcome
    of discussion in \#96}
    \textbf{TOP}
    Approximate run time for \msprime\ simulations,
    for \textbf{(left)} small, and \textbf{(right)} larger simulations.
    Each point is the runtime of one simulation,
    for various values of effective population size ($N$),
    genome length ($L$), and number of samples.
    Runtime scales quadratically with the product of $N$ and $L$;
    since recombination rate in these simulations was $10^{-8}$,
    the scaled recombination rate here is $\rho = NL/10^8$,
    shown on the horizontal axis.
    The black line is a quadratic fit separately in each panel.
    \textbf{BOTTOM}
    Time data from compared with
    equation~\eqref{eqn-hsw-bound} (``expected'').
    Left panel shows observed times plotted against expected number
    of operations; right panel shows the ratio of the two, plotted against $\rho$.
}
\end{figure}

@@

More visibly to the end user, we also have a high standard for documentation,
with precise, comprehensive, and cross-linked documentation
that is automatically built from the code base
and served through the website \url{https://tskit.dev}.
With the goal of lowering the entry barrier to new users,
we have invested significant effort in writing examples and introductions,
and making common tasks discoverable.
We also view contributions to documentation as equally important to the project
as writing code or designing methods---what use would it be
to write reliable, stable software if no-one used it?
